Multidimensional analysis and detection of informative features in human brain white matter

### 2021-02-01 reports/manuscript/paper.tex
Rename notebooks and add plotting notebook
Add comments on comparison to lasso
Remove todo note in abstract

\begin{abstract}
    % Abstracts should be unreferenced and typically around 150 words
    \todo{Shorten abstract to roughly 150 words.}
    The white matter contains long-range connections between different
    brain regions and the organization of these connections holds important
    implications for brain function in health and disease. Tractometry
    uses diffusion-weighted magnetic resonance imaging (dMRI)
    to quantify tissue properties (e.g. fractional anisotropy (FA),
    mean diffusivity (MD), etc.), along the trajectories of these
    connections.
    % \cite{yeatman2012tract}.
    Statistical inference from
    tractometry usually either averages these quantities along
    the length of each bundle in each individual or performs analysis
    point-by-point along each bundle, with group comparisons or regression
    models computed separately for each point along every one of the bundles.
    These approaches are limited in their sensitivity, in the former case, or
    in their statistical power, in the latter.
    In the present work, we developed a method based on the sparse group
    lasso (SGL)
    % \cite{simon2013sparse}
    that takes into account tissue
    properties measured along all of the bundles, and selects informative
    features by enforcing sparsity, not only at the level of individual
    bundles, but also across the entire set of bundles and all of the measured
    tissue properties.
    % The sparsity penalties for each of these constraints
    % is identified using a nested cross-validation scheme that guards
    % against over-fitting and simultaneously identifies the correct
    % level of sparsity.
    We demonstrate the accuracy of the method in two
    settings: i) In a classification setting, patients with amyotrophic
    lateral sclerosis (ALS) are accurately distinguished from matched
    controls.
    % \cite{sarica2017corticospinal}.
    Furthermore, SGL automatically
    identifies FA in the corticospinal tract as important for this
    classification, correctly finding the parts of the white matter known
    to be affected by the disease. ii) In a regression setting, dMRI is
    used to accurately predict ``brain age.''
    % \cite{yeatman2014lifespan, Brown2012-so}.
    In this case, the weights are distributed throughout the
    white matter indicating that many different regions of the white matter
    change with development and contribute to the prediction of age. Thus,
    SGL makes it possible to leverage the multivariate relationship between
    diffusion properties measured along multiple bundles to make accurate
    predictions of subject characteristics while simultaneously discovering
    the most relevant features of the white matter for the characteristic of
    interest.
\end{abstract}

>>>>

\begin{abstract}
    % Abstracts should be unreferenced and typically around 150 words
    The white matter contains long-range connections between different
    brain regions and the organization of these connections holds important
    implications for brain function in health and disease. Tractometry
    uses diffusion-weighted magnetic resonance imaging (dMRI)
    to quantify tissue properties (e.g. fractional anisotropy (FA),
    mean diffusivity (MD), etc.), along the trajectories of these
    connections.
    % \cite{yeatman2012tract}.
    Statistical inference from
    tractometry usually either averages these quantities along
    the length of each bundle in each individual or performs analysis
    point-by-point along each bundle, with group comparisons or regression
    models computed separately for each point along every one of the bundles.
    These approaches are limited in their sensitivity, in the former case, or
    in their statistical power, in the latter.
    In the present work, we developed a method based on the sparse group
    lasso (SGL)
    % \cite{simon2013sparse}
    that takes into account tissue
    properties measured along all of the bundles, and selects informative
    features by enforcing sparsity, not only at the level of individual
    bundles, but also across the entire set of bundles and all of the measured
    tissue properties.
    % The sparsity penalties for each of these constraints
    % is identified using a nested cross-validation scheme that guards
    % against over-fitting and simultaneously identifies the correct
    % level of sparsity.
    We demonstrate the accuracy of the method in two
    settings: i) In a classification setting, patients with amyotrophic
    lateral sclerosis (ALS) are accurately distinguished from matched
    controls.
    % \cite{sarica2017corticospinal}.
    Furthermore, SGL automatically
    identifies FA in the corticospinal tract as important for this
    classification, correctly finding the parts of the white matter known
    to be affected by the disease. ii) In a regression setting, dMRI is
    used to accurately predict ``brain age.''
    % \cite{yeatman2014lifespan, Brown2012-so}.
    In this case, the weights are distributed throughout the
    white matter indicating that many different regions of the white matter
    change with development and contribute to the prediction of age. Thus,
    SGL makes it possible to leverage the multivariate relationship between
    diffusion properties measured along multiple bundles to make accurate
    predictions of subject characteristics while simultaneously discovering
    the most relevant features of the white matter for the characteristic of
    interest.
\end{abstract}
